\documentclass[12pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{tabularx}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}
\renewcommand{\familydefault}{\sfdefault}
\newcolumntype{R}{>{\raggedleft\arraybackslash}X} % create column for contact info table
\newcolumntype{D}{>{\hsize=.75in}X}
\setlength\parindent{0pt}

\begin{document}
%%%%%
\begin{center}
  {\Large  Sean Craig} \par
  Curriculum vitae \par
  \today \par
\end{center}
%%%%%

%%%%%
\begin{tabularx}{\textwidth}{@{}XR@{}}
  4600 Wesley W. Posvar Hall & 810 McCandless Avenue \\
  Pittsburgh, PA 15230 & Pittsburgh, PA 15201 \\
  \href{mailto:sean.craig@pitt.edu}{sean.craig@pitt.edu} & {\tt 330.340.2447} \\
  \href{https://seanmcraig.github.io}{seanmcraig.github.io} & \href{https://github.com/seanmcraig}{github.com/seanmcraig}\\
\end{tabularx} \par\bigskip\bigskip
%%%%%

%%%%%
\section*{\sf Academic Appointments}
\begin{tabularx}{\textwidth}{@{}DX@{}}
  Present & Adjunct Professor, Political Science, University of Pittsburgh \\
  Present & Adjunct Professor, Political Science, La Roche University \\
  2020--2021 & Instructor, Sociology, University of Pittsburgh \\
  2016--2020 & Teaching Fellow, Political Science, University of Pittsburgh \\
  2015--2016 & Teaching Assistant, Political Science, University of Pittsburgh \\
\end{tabularx} \par\bigskip\bigskip

%%%%%
\section*{\sf Education}
\begin{tabularx}{\textwidth}{@{}DX@{}}
  Present & PhD candidate in Political Science, University of Pittsburgh \\
  2016 & MA in Political Science, University of Pittsburgh \\
  2014 & JD, Washington University in St. Louis \\
  2011 & BA in English, Ohio State University \\
\end{tabularx} \par\bigskip\bigskip
%%%%%

%%%%%
\section*{\sf Dissertation in Progress}
\begin{tabularx}{\textwidth}{@{}DX@{}}
  Title: & {\em Understanding Legitimacy in American Local Courts} \\
  Committee: & Chris W. Bonneau (Chair), University of Pittsburgh \\
  & Kristen Kanthak, University of Pittsburgh \\
  & Jonathan Woon, University of Pittsburgh \\
  & Brandon L. Bartels, George Washington University
\end{tabularx} \par\bigskip
%%%%%

%%%%%
\section*{\sf Publications}
%%%%%
\subsection*{\sf Refereed Articles}
\begin{tabularx}{\textwidth}{@{}DX@{}}
  2018 & Woon, Jonathan, Amanda Leifson, Sean Craig, and Matthew Tarpey. %
    ``Trump Is Not a (Condorcet) Loser! Social Choice and the 2016 Republican Nomination.'' %
    {\em PS: Political Science and Politics} 53(3): 407-412. %
    doi:10.1017/S1049096520000359 \bigskip \\
\end{tabularx} \par\bigskip
%%%%%
\subsection*{\sf Law Review Articles}
\begin{tabularx}{\textwidth}{@{}DX@{}}
  2013 & Craig, Sean. %
    ``Juvenile Life Without Parole Post-{\em Miller}: %
    The Long, Treacherous Road Towards a Categorical Rule.'' %
    {\em Washington University Law Review} 91(2): 379-410. \par\bigskip \\
\end{tabularx}
%%%%%
\subsection*{\sf Encyclopedia Entries}
%%%%%
\begin{tabularx}{\textwidth}{@{}DX@{}}
  2017 & Bonneau, Chris W., and Sean Craig. %
  ``{\em Caperton v. A.T. Massey Coal Co.}'' %
  In {\em Encyclopedia of American Civil Rights and Liberties}. 2nd Edition. %
  Edited by Otis H. Stephens, John M. Scheb II, and Kara E. Stooksbury. %
  Santa Barbara, CA: ABC-CLIO/Greenwood. \par\bigskip \\
\end{tabularx}
%%%%%
\subsection*{\sf Other Publications}
\begin{tabularx}{\textwidth}{@{}DX@{}}
  2015 & Bonneau, Chris W., and Sean Craig. %
    ``{\em King v. Burwell} and the Future of the PPACA.'' %
    {\em Retina Today} 10 (May/June): 16-17, 21. \bigskip \\
\end{tabularx} \par\bigskip
%%%%%

%%%%%
\section*{\sf Teaching Experience}

\subsection*{\sf University of Pittsburgh}
American Presidency (Instructor: Spring 2017) \par
Constitution and Civil Liberties (Instructor: Spring 2021) \par
Introduction to American Politics (Assistant: Fall 2015) \par
Public Administration and Political Systems (Instructor: Fall 2017) \par
State and Local Politics (Instructor: Fall 2016) \par
Research Methods in Political Science (Assistant: Spring 2018) \par
Social Research Methods (Fall 2019, Spring 2020) \par

\subsection*{\sf La Roche University}
American Presidency (Instructor: Fall 2020)\par
Introduction to American Politics (Instructor: Spring 2020--2021)

%%%%%
\section*{\sf Conference Activity}

\subsection*{\sf Papers Presented}
%%%%%
\begin{tabularx}{\textwidth}{@{}DX@{}}
  2019 & Craig, Sean. %
    ``Understanding Legitimacy in Local Courts: Building a Measurement Strategy with Millenial Survey Data.'' %
    Annual Meeting of the Midwest Political Science Association. %
    April 4-7. Chicago, IL.
\end{tabularx} \par\bigskip
%%%%%
\begin{tabularx}{\textwidth}{@{}DX@{}}
  2018 & Craig, Sean, and Matthew Tarpey. %
    ``Do Partisan Tides Make Waves in Judicial Elections?'' %
    Annual Meeting of the Southern Political Science Association. %
    January 4-7. New Orleans, LA.
\end{tabularx} \par\bigskip
%%%%%
\begin{tabularx}{\textwidth}{@{}DX@{}}
  2017 & Pronin, Kira, Sean Craig, and Chris W. Bonneau. %
    ``Criminal Courts, Screening of Defendants, and the Right of Appeal.'' %
    Annual Meeting of the Midwest Political Science Association. %
    April 6-9. Chicago, IL.
\end{tabularx} \par\bigskip
%%%%%
\begin{tabularx}{\textwidth}{@{}DX@{}}
  2017 & Craig, Sean. %
    ``Explaining Agency Enforcement Outcomes in the Courts: %
    Evidence from EEOC Litigation, 1997-2006.'' %
    Annual Meeting of the Midwest Political Science Association. %
    April 6-9. Chicago, IL.
\end{tabularx} \par\bigskip
%%%%%
\begin{tabularx}{\textwidth}{@{}DX@{}}
  2017 & Craig, Sean, and Matthew Tarpey. %
    ``Do Partisan Tides Make Waves in Judicial Elections? %
    Governors, Partisanship, and Coattails when Judges Face the Electorate.'' %
    Annual Meeting of the Pennsylvania Political Science Association. %
    March 31-April 1. Robert Morris University.
\end{tabularx} \par\bigskip
%%%%%
\begin{tabularx}{\textwidth}{@{}DX@{}}
  2016 & Craig, Sean. %
    ``Justice Works: Workloads, Resources, and Diffuse Support for Trial Courts %
    in the American States.'' %
    Annual Meeting of the Midwest Political Science Association.'' %
    April 5-8. Chicago, IL.
\end{tabularx} \par\bigskip
%%%%%


%%%%%
\section*{\sf Research Experience}
\begin{tabularx}{\textwidth}{@{}DX@{}}
  2016 & Assistant to Jonathan Woon, University of Pittsburgh (Pedagogy). \\
  2015 & Assistant to Sharece Thrower, University of Pittsburgh (State Governors). \\
  2013-14 & Assistant to Gregory Magarian, Washington University Law (First Amendment). \\
  2013-14 & Assistant to Mae Quinn, Washington University Law (Juvenile Sentencing).
\end{tabularx} \par\bigskip
%%%%%


%%%%%
\section*{\sf Service to Profession}
\begin{tabularx}{\textwidth}{@{}DX@{}}
  2017 & Reviewer, {\em State Politics and Policy Quarterly} \bigskip \\
\end{tabularx} \par\bigskip
%%%%%


%%%%%
\section*{\sf Courses Prepared to Teach}
American Presidency \par
Constitution Law\par
Civil Liberties\par
Introduction to American Politics \par
Judicial Politics \par
Legal Writing \par
Quantitative Research Methods \par
State Politics \par
%%%%%

%%%%%
\section*{\sf Technical Skills}
\begin{tabularx}{\textwidth}{@{}lX@{}}
Data Visualization: & {\tt ggplot2} \\
Document Markup: & \LaTeX, Markdown \\
Programming: & Bash, some Python \\
Statistical Computing: & R, Stata \\
Other Competencies: & Github, some experience with Qualtrics, z-Tree
%%%%%

\end{tabularx}

\end{document}